---
title: "Homework 1"
author: "David Chester"
date: "8.28.2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, commen = NA)
```

## Task 1

```{r mh_distance_function}
x<-FALSE
y<-FALSE
distance<-0
options(warn=0)
the_hamming_distance<-0
mh_distance <- function(x,y){
  if(!is.atomic(x)){
    warning('x is not atomic')
    return(-1)
  }
  if(!is.atomic(y)){
    warning('y is not atomic')
    return(-1)
    # note; we are told we are given atomic vectors for our inputs.
    # note; vectors are atomic in R, and if, say, we had c("cat", 9), 
    # R would coerce this vector (by definition of vectors in R) to be 
    # atomic...it will be of type character. 
    # To my knowledge, we cannot discern if the original elements of the 
    # argument vectors are, in fact, all of the same type...
    # So, no matter what our vector is, we will always get past this first check
    # Lastly, by the description in the task, we are told the vector inputs
    # are atomic. 
  }
  if(length(x)!=1){
    warning('x is not length one')
    return(-1)
  }
  if(length(y)!=1){
    warning('y is not length one')
    return(-1)
  }
  if((is.na(x)|is.nan(x)|is.infinite(x))){
    warning('x is cannot be NA, Nan, Inf, -Inf')
    return(-1)
  }
   if((is.na(y)|is.nan(y)|is.infinite(y))){
    warning('y is cannot be NA, Nan, Inf, -Inf')
    return(-1)
  }
  if(!(is.numeric(x)|is.logical(x)|is.character(x))){
    warning('x is not of type logical, numeric, or character')
    return(-1)
  }
  if(!(is.numeric(y)|is.logical(y)|is.character(y))){
    warning('y is not of type logical, numeric, or character')
    return(-1)
  }
  if(typeof(x)!=typeof(y)){
    warning('y and x are not of the same type')
    return(-1)
  }
  if(typeof(y)=="numeric"){
    if(y %% 1!=0){
      warning('y contains decimals')
      return(-1)
    }
  }
  if(typeof(x)=="numeric"){
    if(x %% 1!=0){
      warning('x contains decimals')
      return(-1)
    }
  }
  if(typeof(x)=="logical"&typeof(y)=="logical"){
    if(x!=y){
      distance<-1
    }
    return(distance)
  }
  x_string<-toString(x) 
  y_string<-toString(y) 
  x_string<-toString(x) 
  y_string<-toString(y) 
  x_string_split<-strsplit(x_string,"")
  y_string_split<-strsplit(y_string,"")
  unlist_x_string_split<-unlist(x_string_split)
  unlist_y_string_split<-unlist(y_string_split)
  if(length(unlist_x_string_split)!=length(unlist_y_string_split)){
    warning('x and y do not have the same number of digits or letters')
    return(-1)
  }
  for(i in seq_along(unlist_x_string_split)){
    if(length(setdiff(unlist_x_string_split[i],unlist_y_string_split[i]))==1){
      distance<-distance+1
    }
  }
  return(distance)
}
mh_distance(x,y)


# A note, when I run this code in my local machine, I get:
# Warning in mh_distance(x, y) :
#  x is not of type logical, character, or numeric
# Warning in mh_distance(x, y) :
#  y is not of type logical, character, or numeric

# However, when I run it on the server, I get:
# x is not of type logical, character, or numericy is not of type logical, character, or numeric

# I imagine this has to do with the different versions (server = 3.6.1, and local = 4.0.2)
```

```{r}

```



## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return non-negative modified Hamming distance)

```{r eval=FALSE}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
# additional test cases go here
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
# additional test cases go here
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
# loop goes here
```


## Task 4

Brief write-up goes here...
