---
title: "Homework 1"
author: "David Chester"
date: "8.28.2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, commen = NA)
```

## Task 1

```{r mh_distance_function}
x<-FALSE
y<-FALSE
distance<-0
#nothing
options(warn=0)
the_hamming_distance<-0
mh_distance <- function(x,y){
  if(!is.atomic(x)){
    warning('x is not atomic')
    return(-1)
  }
  if(!is.atomic(y)){
    warning('y is not atomic')
    return(-1)
    # note; we are told we are given atomic vectors for our inputs.
    # note; vectors are atomic in R, and if, say, we had c("cat", 9), 
    # R would coerce this vector (by definition of vectors in R) to be 
    # atomic...it will be of type character. 
    # To my knowledge, we cannot discern if the original elements of the 
    # argument vectors are, in fact, all of the same type...
    # So, no matter what our vector is, we will always get past this first check
    # Lastly, by the description in the task, we are told the vector inputs
    # are atomic. 
  }
  if(length(x)!=1){
    warning('x is not length one')
    return(-1)
  }
  if(length(y)!=1){
    warning('y is not length one')
    return(-1)
  }
  if((is.na(x)|is.nan(x)|is.infinite(x))){
    warning('x is cannot be NA, Nan, Inf, -Inf')
    return(-1)
  }
   if((is.na(y)|is.nan(y)|is.infinite(y))){
    warning('y is cannot be NA, Nan, Inf, -Inf')
    return(-1)
  }
  if(!(is.numeric(x)|is.logical(x)|is.character(x))){
    warning('x is not of type logical, numeric, or character')
    return(-1)
  }
  if(!(is.numeric(y)|is.logical(y)|is.character(y))){
    warning('y is not of type logical, numeric, or character')
    return(-1)
  }
  if(typeof(x)!=typeof(y)){
    warning('y and x are not of the same type')
    return(-1)
  }
  if(is.numeric(x)){
    if(x %% 1!=0){
      warning('x contains decimals')
      return(-1)
    }
  }
  if(is.numeric(y)){
    if(y %% 1!=0){
      warning('y contains decimals')
      return(-1)
    }
  }
  if(typeof(x)=="logical"&typeof(y)=="logical"){
    if(x!=y){
      distance<-1
    }
    return(distance)
  }
  x_string<-toString(x) 
  y_string<-toString(y) 
  x_string<-toString(x) 
  y_string<-toString(y) 
  x_string_split<-strsplit(x_string,"")
  y_string_split<-strsplit(y_string,"")
  unlist_x_string_split<-unlist(x_string_split)
  unlist_y_string_split<-unlist(y_string_split)
  if(length(unlist_x_string_split)!=length(unlist_y_string_split)){
    warning('x and y do not have the same number of digits or letters')
    return(-1)
  }
  for(i in seq_along(unlist_x_string_split)){
    if(length(setdiff(unlist_x_string_split[i],unlist_y_string_split[i]))==1){
      distance<-distance+1
    }
  }
  return(distance)
}
mh_distance(x,y)


# A note, when I run this code in my local machine, I get:
# Warning in mh_distance(x, y) :
#  x is not of type logical, character, or numeric
# Warning in mh_distance(x, y) :
#  y is not of type logical, character, or numeric

# However, when I run it on the server, I get:
# x is not of type logical, character, or numeric

# I imagine this has to do with the different versions 
# (server = 3.6.1, and local = 4.0.2)

# In either case, the local pdf knit and server pdf knit 
# produces the same document
```



## Task 2


**Initial test cases** (return non-negative modified Hamming distance)

```{r}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
# These provide the output desired
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
mh_distance(x="toy",y="xan")
mh_distance(x=T, y=TRUE)
mh_distance(x=F, y=TRUE)
mh_distance(x=10010,y=11111)
```

**Initial test cases** (return values of `-1`)

```{r}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
# I got one here, so my decimal check is not working
# Switched from typeof(x)=="numeric" to is.numeric(x)
# Issue solved
```

Added test cases that return a value of `-1`.

```{r}
mh_distance(x=as.complex(5),y=2)
mh_distance(x=87, y="87")
mh_distance(x=878, y=87)
mh_distance(x=00010,y=11111)
# Note that the last line gives an error.
# In r if we assign 010 to an object, it will be stored as 10 not 010. 
# I do not see this is a special case we need to treat
# because this is a known property of R to be considered prior
# to providing the arguments to the function.
# In other words, you can't assign 00010 to x as a numeric no matter what.
# One can use sprintf or formatC but these just convert to string type anyway.
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
x<-c("cat", "dog", "horse", "fish")
y<-c("cat", "hog", "houses", "chip")
modified_vectorized_mh_distance<-function(x,y){
print_line<-rep(NA, length(x))
result<-rep(NA, length(x))
if(length(x)!=length(y)){
  warning('x and y are of different vector lengths')
  return(-1)
  }
for(i in seq_along(x)){
  result[i]<-mh_distance(x[i],y[i])
  }
for(i in seq_along(x)){
  print_line[i]<-paste0("The", " modified", " Hamming", " distance", " between ", 
                        x[i], " and ", y[i], " is ", result[i])
  }
for(i in seq_along(x)){
  print(print_line[i])
}
}
modified_vectorized_mh_distance(x,y)

```

```{r}
# If any results are -1, then proceed to evaluate the issue 
# by checking mh_distance(x,y)
# This may be necessary if there a multiple lines printing -1 
# For example; 
mh_distance(x="horse",y="houses")
# produces a warning that x and y do not have the 
# same number of digits or letters
```

```{r}
modified_vectorized_mh_distance(s,w)
```


## Task 4

As mentioned in lecture, our code does not handle NULL values or values with special characters included in words like "can't" etc. We are robust, however, to complex number inputs. 

For task one, my approach consisted of first handling all the checks before constructing the mh_distance. Note there is a discussion on atomic vectors included early on, but does not truly apply until task 3. 

After checking for length, NA, NaN, Inf, -Inf, logical, numeric, or character, I then checked for decimals and for logical equivalence.

I noted that it was also important to switch my options(warn=0) to obtain the output I was hoping for. However, I found conficting output syntax between working on the server and working on my local machine. Luckily, the output of the knited pdf document was the same for both. 

Constructing the distance calculation required converting whatever object x and y were to strings, then spliting them by character, then unlisting them. This allowed for comparing the length of the characters between the two (I'm sure I could have used nchar() as well). From here I used a for loop utilizing seq_along as opposed to length to avoid certain looping errors. 

I think the key component for getting my distance functio to work consisted of using setdiff and length. Set diff for multiple elements provides how many different elements exist between two sets. However, if I input just sets of length one each, the only possible return is 0 or 1. In the event that the lenght of my set difference was one for each character comparison of x[i], y[i], I would add 1 to my distance. 

